---
title: 'Prepare Data - S2'
author: 
output: 
  github_document:
    toc: yes
always_allow_html: true
editor_options: 
  
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
#renv::snapshot()
```

## Tidy Data
```{r "get & clean data", results="hide"}
source(here("src/data-processing/get_data.R"))
```


# Construction of variabeles
## Data
Filter data for resspondents that partipated `=< 3`.
```{r "filter"}
n <- d %>% 
  group_by(id) %>% 
  count() %>% 
  filter(n>=3 & n<6) %>% 
  ungroup() 

d <- left_join(n, d, by = "id") %>% 
  select(-n)
```

## Sociale Media Usage (I1_5) 
Categories

1. social media higher than average & other media higher than average (news junkies)
2. social media higher than average & other media lower than average (SM news users)
3. social media lower than average & other media higher than average (traditional news users)
4. social media lower than average & other media lower than average (news avoiders)

## Political Sentiment
1. Anxiety (0/1)
2. Anger is constructed by respondents answering either Loathing or Distrust (0/1)


## Volatility
Types:

1. Conversion-inter: changing intention to vote w1-w4 (change during campaign ) between the "blocks" 
2. Conversion-intra: changing intention to vote w1-w4 (change during campaign ) within the "block" 
3. Conversion-choiceset: changing intention to vote w1-w4 (change during campaign ) within choice set based on PTV
4. Cristalization-inter: change between vote choice (w5) and last vote intention between the "blocks"
5. Cristalization-intra: change between vote choice (w5) and last vote intention within the "block"
6. Cristalization-choiceset: change between vote choice (w5) and last vote intention within choice set based on PTV
7. Consolidation-inter: change between vote choice 2021 and 2023 between the "blocks"
8. Consolidation-intra: change between vote choice 2021 and 2023 within the "block"
9. Consolidation-choiceset: change between vote choice 2021 and 2023 within choice set based on PTV

```{r "operationalization"}
source(here("src/data-processing/operationalization_S2.R"))
save(df, file = here("data/intermediate/cleaned_data_allwaves.RData"))
rm(d)
```

# Data Description

## Sociale Media Use
Who is in which category?

```{r "descr-sm-s2", fig.width=10, fig.height=15}
source(here("src/data-processing/descr_sm_s2.R"))
p1 
p2 
p3

k1 <- p3
rm(p1, p2, p3, tmp)
```

## Political Sentiment
Wich people experience what political sentiment?

```{r "descr-emoties-s2", fig.width=6, fig.height=6}
source(here("src/data-processing/descr_emotion_s2.R"))
p1
k2 <- as.list(p1)
rm(p1, tmp)
```

## Volatility
Which people are in what category? (for all types of volatilitym choice-set is overlapping with inter- or intra-block)

```{r "descr-vol-s2", fig.width=10, fig.height=15}
source(here("src/data-processing/descr_vol_s2.R"))
p1 #demografisch profiel obv conversie 
p1b #demografisch profiel obv conversie (choice set)
p2 #profiel poltieke achtergrond obv conversie
p2b #profiel poltieke achtergrond obv conversie (choice set)

p3 #profiel poltieke achtergrond obv kristalisatie
p3b #profiel poltieke achtergrond obv kristalisatie (choice set)
p4 #profiel poltieke achtergrond obv kristalisatie
p4b #profiel poltieke achtergrond obv kristalisatie (choice set)

p5 #profiel poltieke achtergrond obv versteviging
p5b #profiel poltieke achtergrond obv versteviging (choice set)
p6 #profiel poltieke achtergrond obv versteviging
p6b #profiel poltieke achtergrond obv versteviging (choice set)

p7
k3 <- p7

kableExtra::kbl(tab, booktabs =T, caption = "\\label{tab:conditions} # Respondents per Volatility Category") %>%
  kableExtra::kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  kableExtra::column_spec(1, width = "8cm") %>%
  kableExtra::column_spec(2, width = "2cm")

rm(p1, p2, p3, p4, p5, p6, p7, p1b, p2b, p3b, p4b, p5b, p6b, tmp, tab)
```

```{r "descr", fig.width=15, fig.height=8}
k1 + as.list(k2) + k3

rm(k1, k2, k3)
```