---
title: 'Prepare Data - S1'
author: 
output: 
  github_document:
    toc: yes
always_allow_html: true
editor_options: 
  
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
#renv::snapshot()
```

## Tidy Data
```{r "get & clean data", results="hide"}
source(here("src/data-processing/clean_eves.R"))
```

# Construction of variabeles

## Sociale Media Usage (I1_5) 
Categories

1. social media higher than average & other media higher than average (news junkies)
2. social media higher than average & other media lower than average (SM news users)
3. social media lower than average & other media higher than average (traditional news users)
4. social media lower than average & other media lower than average (news avoiders)

## Political Sentiment
1. Anxiety (0/1)
2. Anger is constructed by respondents answering either Loathing or Distrust (0/1)


## Volatility
1. Inter-block: change between vote choice and vote intention between the "blocks"
2. Intra-block: change between vote choice and vote intention within the "block"
3. choiceset: hange between vote choice and vote intention  within choice set based on PTV

```{r "operationalization"}
source(here("src/data-processing/party_harmonisation.R"))
source(here("src/data-processing/operationalization_S1.R"))
save(d1, file = here("data/intermediate/cleaned_eves.RData"))
```

# Data Description

## Sociale Media Use
Who is in which category?

```{r "descr-sm-s1", fig.width=10, fig.height=15}
source(here("src/data-processing/descr_sm_s1.R"))
p1 
```

```{r "descr-sm-s1-2", fig.width=10, fig.height=10}
p2
rm(tmp, p1, p2, countries)
```

## Political Sentiment
Wich people experience what political sentiment?

```{r "descr-emoties-s1", fig.width=10, fig.height=15}
source(here("src/data-processing/descr_emotion_s1.R"))
p1 #demografisch profiel obv woede 
p2 #demografisch profiel obv angst
p3 #political sentiment accross europe

rm(p1, p2, p3, tmp, fig_cols2)
```

## Volatility
Which people are in what category? (for all types of volatility choice-set is overlapping with inter- or intra-block)

```{r "descr-vol-s1", fig.width=10, fig.height=15}
source(here("src/data-processing/descr_vol_s1.R"))
p1a #demografisch profiel obv intra /inter
p1b# #demografisch profielobv cs
```

```{r "descr-vol-s1-2", fig.width=10, fig.height=8}
p2  #volatiliteit door europa

rm(p1a, p1b, p2, countries, tmp)
```
